\recepient{Prof. Marek Płoszajczak\\GANIL\\Caen, France}
\subject{Application as postdoctoral fellowship in theoretical nuclear physics at GANIL}
\coverletter[sender=false, vspace=4mm]

Dear Prof. Marek Płoszajczak,\\

I want to introduce myself as an applicant for the postdoctoral position at GANIL. I am excited about this potential opportunity to develop and deepen my knowledge of nuclear physics, the Gamow shell model in particular, as well
as working at an international institution such as GANIL, where physics happens. This postdoc position would be a primary goal for my career and personal life. \\

During my current Ph.D. with Prof. Rodolfo Id Betan as my supervisor, I am working with the Gamow shell model to describe the alpha decay of the nuclei Polonium-212, Tellurium-104, and Titanium-44. The theoretical framework includes, among others, the two-body force with a Gaussian interaction. Also, the spectroscopic factor is calculated with the norm kernel correction. \\

In addition, since 2021, I have been part of a project with colleagues from an information and system sciences institute seeking to achieve the nuclear drip line by using mathematical and statistical methods, which gives me more computational skills and interdisciplinary work experience. Furthermore, I collaborated on a divulgation article on nuclear resonance aimed at undergraduate students. \\

This experience has given me various computer and physical skills, along with the ability to work independently and in a group. My profile and experience with the Gamow Shell Model (GSM) formalism and various programming skills make me a suitable candidate for the postdoctoral position you are offering.
Now a day, I do not have experience with reaction theory, but I can quickly learn. Besides, I am familiar with the GSM code since I use it to benchmark my four-body code. \\

On a personal level, I want to let you know that I have been a kidney transplant recipient since March 2022. I have a normal everyday life except for my medication and a bimonthly medical control. The Argentinian government and my health insurance provides the medicine. If I have the privilege to work at GANIL, I will travel with the necessary medication and the recommended medical contacts. \\

I appreciate your consideration as a candidate and hope to fulfill your expectations. I look forward to hearing from you and the project. \\

Sincerely, 
